### 2020-11-03 treatise/1_introduction.tex
Update figures

The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in another basis.
(Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
In the given basis, more measurements are required to recover the signal, while fewer suffice in the sparse basis.
But, even if we are guaranteed a sparse basis exists, it is still a nontrivial undertaking to construct it.

A series of investigation started when Candès and Tao \cite [Can05].
Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
%
\DispNum {y:y:Qx:Qx} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
Certainly, \m {\M {Q} \RB {\V {x} - \V {x}'} = 0}, then \m {\V {x}, \V {x}'} are indistinguishable.
But if \m {\V {x}} is sparse, it essentially restrict the system so much that we obtain unique solution for most of the time.

@@

Candès and Tao showed that (\It {ibid}), in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.

As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis (\It {ibid}).

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero-position of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

Ever since, OMP has since been applied in a variety of ways.
Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.

Some further attempts include Manoj and Kannu \cite [MaK17], which formulate the sparse condition as overlapping block in the reconstructed signal, and encode possible blocks.
Gurbuz, Yapici, and Guvenc \cite [GYG18] introduce perturbation of the quantized set of angles, on which the sensing matrix is based.
Most recently, Panayirci et.\ al.\ \cite [PAU19] put forward a more thorough treatment, where in addition to application of OMP, they use a first stage of max-likelihood estimation of model parameters, and a second stage of maximum-a-posteriori estimation of channel gains.

Performance guarantee of OMP is also studied, by refining or proposing different conditions.
Cai, Wang, and Xu \cite [CWX10], under assumption on low coherence of columns of matrices, give new bound on OMP.
Coherence-based assumptions, instead of almost-unitarity, make the condition easier to verify.
Cai and Wang \cite [CaW11] extends the investigation to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] follow up and refine their bounds, and conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.

@@

From above we note that work on channel estimation seems to favored OMP for its low complexity.
One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
In addition, the assumption that the channel matrix is sparse, at least, warrant justification.

In this treatise, we argue that DS is worth trying as an alternative.
As the next section shows, the effective beamformer serves readily as the sensing matrix with RIP.
Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
Along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of on the sparsity and the number of paths, which will surely faciliate system design.
We show that it holds under an overwhelming probability, which is also bounded quantitatively.

Moreover, we illustrate that the convex program is equivalent to a linear program, for which several efficient algorithms are known.
In view of numerical results, DS is often superior to OMP among other methods, at the cost of higher complexity.

>>>>

The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in transformed basis.
(Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
But, even if we are guaranteed latter basis exists, it is still a nontrivial undertaking to construct it.

Candès and Tao \cite [Can05] first embarked a series of investigation on the problem.
Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
%
\DispNum {y:y:Qx:Qx} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
Certainly, \m {\M {Q} \RB {\V {x} - \V {x}'} = 0}, then \m {\V {x}, \V {x}'} are indistinguishable.
But if \m {\V {x}} is sparse, it essentially restrict the system so much that we obtain unique solution for most of the time.

@@

Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.

As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis \cite [CaT07].

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
%
\item Initialize
%
\Disp {
\NC \V {r}
\LA \NC \V {y} \NR
%
\NC S
\LA \NC \varnothing \NR
}
\item Start the loop with counter \m {i \LA 1}.
\item Find
%
\DispNum {c:c:i0:ir} {
\NC c
\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
}
%
and insert \m {S \LA S \cup {i}}.
\item Compute
%
\DispNum {Q:Q:QS:Qy} {
\NC \M {Q} ^\ddagger
\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
%
\NC \V {r}
\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
}
\item Break if
%
\DispNum {r:2:h':h'} {
\NC \VNm {\V {r}} _2
<\NC \eta \NR
}
%
where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
\item Output 
%
\DispNum {g:g:Qy:Qy} {
\NC \Hat {\V {g}}
\LA \NC \M {Q} ^\ddagger \V {y} \NR
}
\stopitemize
}
%
Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

OMP has since been applied widely in the literature.
Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discussed the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero components.
Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, with the effective beamformer serving as sensing matrix, where set of quantized angles was specially designed, and permuted DFT matrix is used.

Some further attempts include Manoj and Kannu \cite [MaK17], who formulated the sparse condition on submatrices of the signal for successful reconstruction.
Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation of the quantized set of angles, on which the sensing matrix is based.
Panayirci et.\ al.\ \cite [PAU19] suggested, in addition to application of OMP, a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains.

Performance guarantee of OMP is also studied on various conditions.
Cai, Wang, and Xu \cite [CWX10], under assumption of low coherence of columns of matrices, instead of almost-unitarity, gave new bound on OMP.
Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low-SNR scenario, and DS is better for high-SNR.

@@

From above we note that work on channel estimation seems to favored OMP for its low complexity.
One notable difficulty in channel estimation is that, in the uniform linear array setting, the quantized angle of arrival and departure, which the sensing matrix is based on, does not necessarily match the true ones \cite [GYG18].
Also, as the nature of OMP is greedy, and it is not clear whether it achieves optimality, and the assumption that the channel matrix is sparse warrant justification too.

In this treatise, we suggest DS as an alternative.
Chapter 2 shows, the effective beamformer may serve as the sensing matrix with RIP.
Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
In chapter 3, along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of the sparsity and the number of paths.
We claim that the bound holds for overwhelming probability.
In chapter 4, we remark that DS can be written as an linear program, for which efficient algorithms are known.
We present numerical results, which show that DS is often superior to OMP among other methods, which is achieved at the cost of higher complexity.

### 2020-11-03 treatise/4_simulation.tex
Update figures

In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
%
\blank [big]
%\externalfigure [assorted-wide-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]

As of the plot of time taken in minutes, we give only one of \m {N_H = 12}, as an example.
%
\blank [big]
\externalfigure [assorted-small-time.png] [wfactor=fit, hfactor=fit]

@@

Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
Here, the bound \m {\T {\chi}} is shown.

%
\blank [big]
%\externalfigure [ddss-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]

@@

%
\blank [big]
%\externalfigure [oommpp-very-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
%\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
%
\blank [big]
\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]

@@

Our \m {\T {\chi}}, unfortunately, does not agree the simulated error of DS, and the matter remains to be investigated in the future.
As pointed above, the simulated error is very constant around 1, so \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3 (despite our effort to estimate), and thus the validity of performance guarantee of DS becomes more dubious.

@@

To give some idea when DS works or not, the figure above illustrates a case where DS failed.
We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
Subsequent application of DS on the wrong index set fails, as a result.

>>>>

In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24} (from ``very small'' to ``very big''), respectively.
Plots 1 to 5 have \m {N_H = 3 N_Y} (``narrow''), and the plots 6 to 10 has \m {N_H = 2 N_Y} (``wide'').
%
Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
\blank [big]
\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
\blank [big]
\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 2 N_Y, N_H = 12}, error:
\blank [big]
\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 2 N_Y, N_H = 16}, error:
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 2 N_Y, N_H = 20}, error:
\blank [big]
\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 2 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]

As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]

@@

Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
Here, the bound \m {\T {\chi}} is shown.
%
Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
\blank [big]
\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
\blank [big]
\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
\blank [big]
\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]

@@

%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
%
Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
\blank [big]
\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
%
As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
%
\blank [big]
\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]

@@

Our \m {\T {\chi}}, 
It is not clear, unfortunately, why the simulated error \m {\T {\chi}} does not agree the simulated error \m {\chi} of DS, and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
The matter remains to be investigated in the future.
As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.

@@

To give some idea of the case that DS works or fails, the figure above illustrates a case where DS failed.
We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
Subsequent application of DS on the wrong index set fails, as a result.

### 2020-11-03 treatise/5_conclusion.tex
Update figures

This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
We motivated the problem, and provided a rather broad survey of recent literature.
This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
Rather than exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.

Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Candès and Tao \cite [CaT07], that for overwhelming probability, the expected square error is bounded.

We also point out that DS may be cast into an LP, and simulation is done.
DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
Unfortunately, the program is prone to give overflown output, and we have not investigated range of parameter extensive enough for more conclusions.

Considering analytical bounds, it can be not easy to give meaningful comparison of existent bounds for these algorithms, as their settings are somewhat different, which we ought to keep in mind.
Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), there do not seem to be much analysis.
and that (to add to complication) is still different from RIP.

OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which one is universally better than the other.
The investigation eloquently illustrates the fact that different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.

>>>>

The treatise addresses the problem of effective estimation of the millimeter wave channel by exploiting its sparsity.
Towards that end, we try the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is a more common choice, as the estimation algorithm.
We proceed by exploiting the sparsity of spatial frequency domain, rather than 
the spatial domain itself, and suggested the generalization of DS for complex vectors work in present case.
Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Candès and Tao \cite [CaT07], that for overwhelming probability, the expected square error is bounded.

We also point out that DS may be cast into an LP, and simulation is done.
DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
Unfortunately, , and it remains to investigate why there is no obvious trend between the signal level and the relative error norm, and a wider range of parameter has to be tried for further conclusions.
We also point out the Python package CVXPY sometimes gives overflown values.

One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
OMP, on the other hand, requires only an entrywise i.i.d.\ Normal sensing matrix \cite [TrG07a], but much analysis remains to be done.
OMP trades off precision for a lower time and space complexity, and for DS the other way around, and this eloquently illustrates that different technique suits different problems and constraints, as is true in every discipline of engineering.
